\chapter{Sprint 2 - DXF to GCODE}
	\label{chap:background}
		
	After completing the background research, the first thing to be worked on was the conversion of a DXF file into basic GCODE instructions.

	\section{Safety Critical Systems}
		The first section which required research was safety critical systems. This was the main topic of the dissertation and there was no prior knowledge of the topic going into the project. This meant that a lot of prior research was required in order to ensure the system followed a safety critical level design, implementation and testing.

	\section{GCODE}
		\label{sec:google_fu}
		The internet is big \cite{sizeofinternet}. Knowing how to phrase a question to a search engine is therefore an invaluable skill. If the request is simple enough, even a poorly structured query will likely return usable results. For more difficult to find resources you can leverage the language of the search engine to gather relevant papers and resources for your research more efficiently. 
		
		% An example of how to center a passage of text, control local fontsize, 
		% and create a properly formatted and clickable URL.
		\begin{center}
		{\small \url{https://www.gwern.net/Search}}
		\end{center}
		
		``Internet Search Tips'' \cite{gwern} provides an excellent review of methods and tips for scouring the internet for hard to find resources. You will also be less likely to get caught behind journal paywalls when working remotely without a tunnel as your queries can be made to look for raw pdfs that are often released by the authors directly.
			
	\section{Organizing your citations in BibTeX}       
		\label{sec:resources_bibtex}
	
		BibTeX is a language for specifying resource citations. Every time you access and read an academic paper, take code from an online repository, or source the media such as images from existing works you should create a BibTeX entry in a file that you keep throughout your research. Software such as Mendeley \cite{mendeley} can help automate the process of building your BibTeX library of citations. 
		
		\lstinputlisting[label={lst:bibtex}, caption={An example BibTeX entry for an academic paper published in conference proceedings \cite{kaj86}.}]{./listings/example_bibtex.bib}
		
		The BibTeX code listing above (listing \ref{lst:bibtex}) shows an example of how to cite an academic paper, in this case one of the central papers in Computer Graphics research. The key \textbf{kaj86} is an arbitrary name chosen as a meaningful identifier for the resource. In the document text we can call on this resource as an inline citation using the LaTeX command \lstinline|\cite{kaj86}| which produces \cite{kaj86} at the location it is called. As long as a citation has been used at least once somewhere within the document then a formatted full citation will be created in the bibliography at the end of the document with the same citation number that is shown inline.
		
		It is considerably easier to be disciplined in methodically taking note of the resources you access and make use of as you access them, than it is to try and hunt them all down again at the time you need to write about them in your document. Invest time in being organized and consistent up front and it will be easier when you come to write up.
		
	\section{DXF}
		Usually you would not put the URL of the resource you are citing directly in the text like is done previously in section \ref{sec:google_fu}. The citation for the resource \cite{gwern} is sufficient to reference it within the text given that full details of its location are then kept neatly within the bibliography at the end of the document. 
		
		In normal usage the purpose of a citation is not to direct the reader away from your thesis, but to justify and back up assertions you are making about the state of the domain. If a reader questions your assertions then they can follow the rabbit hole of papers which will likely also make and justify assertions with even earlier papers from the literature. 
		
		In the above case the intention is for the reader of this template to actually go to that resource and read what it has to say directly. The link is therefore shown clearly within the main text to indicate that the reader should visit it. This as opposed to wanting the reader to purely acknowledge that the facts which are within the resource legitimize the points made in this document, in which case a simple inline citation is the best way to back up your assertions. Section \ref{sec:typesetting_figures_citation} specifically touches on the best practice for how to cite images which you are importing from existing work. 